SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-08 abs.tex
minor
Typo. Had corrected in the submitted paper

In this paper, we introduce Perceptron-based Prefetch Filtering
(PPF) as a way increase the coverage of the prefetches generated by
a baseline prefetcher without negatively impacting accuracy. PPF
enables more aggressive tuning of a given baseline prefetcher,
leading to increased coverage by filtering out the growing numbers
of inaccurate prefetches such an aggressive tuning implies. We also
explore a range of features to use to train PPF's perceptron layer
to identify inaccurate prefetches. PPF improves performance on a
memory-intensive subset of the SPEC CPU 2017 benchmarks by 3.78\%
for a single-core configuration, and by 11.4\% for a 4-core
configuration, compared to the baseline prefetcher alone. We also
show that performance continues to scale as the number of cores
sharing a last level cache increases.

>>>>

  In this paper, we introduce Perceptron-based Prefetch Filtering
  (PPF) as a way to increase the coverage of the prefetches generated by
  a baseline prefetcher without negatively impacting accuracy. PPF
  enables more aggressive tuning of a given baseline prefetcher,
  leading to increased coverage by filtering out the growing numbers
  of inaccurate prefetches such an aggressive tuning implies. We also
  explore a range of features to use to train PPF's perceptron layer
  to identify inaccurate prefetches. PPF improves performance on a
  memory-intensive subset of the SPEC CPU 2017 benchmarks by 3.78\%
  for a single-core configuration, and by 11.4\% for a 4-core
  configuration, compared to the baseline prefetcher alone.
